**Title**

### 2018-07-16 manuscript_draft.Rmd
further analyses

---
title: "**Title**"
author: "$^{1}$Petr Capek*, $^{1}$Katherine Todd-Brown, $^{1}$Natalie Sadler, $^{1}$Nancy Hess, $^{1}$Kirsten Hofmockel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontfamily: mathpazo
fontsize: 11pt
bibliography: mint.bib
output: 
  pdf_document
header-includes:
    - \usepackage{setspace}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
    - \usepackage{titling}
    - \pretitle{\begin{flushleft}}
    - \posttitle{\end{flushleft}}
    - \preauthor{\begin{flushleft}\large}
    - \postauthor{\par\end{flushleft}}
    - \predate{\begin{flushleft}}
    - \postdate{\par\end{flushleft}\vskip 0.5em}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

---
title: "**Title**"
author: "$^{1}$Petr Capek*, $^{1}$Katherine Todd-Brown, $^{1}$Natalie Sadler, $^{1}$Nancy Hess, $^{1}$Kirsten Hofmockel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontfamily: mathpazo
fontsize: 11pt
bibliography: mint.bib
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
    - \usepackage{titling}
    - \pretitle{\begin{flushleft}}
    - \posttitle{\end{flushleft}}
    - \preauthor{\begin{flushleft}\large}
    - \postauthor{\par\end{flushleft}}
    - \predate{\begin{flushleft}}
    - \postdate{\par\end{flushleft}\vskip 0.5em}
    - \usepackage{float}
    - \floatplacement{figure}{H}

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=40),tidy=TRUE)

library(knitr)
library(ggplot2)
library(grid)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)

theme_min<-theme(axis.text.x=element_text(vjust=0.2, size=14, colour="black"),
                 axis.text.y=element_text(hjust=0.2, size=14, colour="black"),
                 axis.title=element_text(size=14, colour="black"),
                 axis.line=element_line(size=0.5, colour="black"),
                 strip.text=element_text(size=16, face="bold"),
                 axis.ticks=element_line(size=1, colour="black"),
                 axis.ticks.length=unit(-0.05, "cm"),
                 panel.background=element_rect(colour="black", fill="white"),
                 panel.grid=element_line(linetype=0),
                 legend.text=element_text(size=14, colour="black"),
                 legend.title=element_text(size=14, colour="black"),
                 legend.position=c("right"),
                 legend.key.size=unit(1, "cm"),
                 strip.background=element_rect(fill="grey98", colour="black"),
                 legend.key=element_rect(fill="white", size=1.2),
                 legend.spacing=unit(0.5, "cm"),
                 plot.title=element_text(size=28, face="bold", hjust=-0.05))

```

@@

##Tables
```{r Tab. 1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, results='asis'}
#tab1<-rbind(decay_all_results$likelihood, monod_all_results$ll_r, mem_all_results$ll_r,
            #mend_all_results$ll_r, mmem_all_results$ll_r)
#colnames(tab1)<-c("_Log Likelihood_", "_N_", "_R^{2}_", "_AIC_")
#rownames(tab1)<-c("First order decay", "Monod growth", "MEM", "MEND", "MMEM")
#write.csv(tab1, "./tab1.csv")

tab1<-read.csv("tab1.csv")
colnames(tab1)<-c(" ", "_Log Likelihood_", "_N_", "_R\\textsuperscript{2}_", "_AIC_")

kable(tab1, align='c', digits=c(0, 1, 0, 2, 1), caption = "_Correspondence between measured resiration rate and respiration rate modeled by five different models (First order decay, Monod growth, two different Microbial Enzyme Models (MEM and MEND) and Metabolic Microbial Enzyme Model (MMEM)). Log Likelihood, coefficient of determination ($R^{2}$), Akaike Information Criterion (AIC) and the number of estimated parameters are reported. All models are calibrated against measured respiration rate only._")
```

##Figures

```{r Scheme 1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

scheme<-"digraph all{

graph [overlap = false, fontsize = 10, layout = dot, rankdir = LR, penwidth = 0.001, root = cluster1];

subgraph cluster0{

graph [overlap = false, fontsize = 10, layout = dot, rankdir = LR];

#nodes

node [shape = circle];
f [label = 'C@_{S}'] ;
g [label = 'C@_{MB}'];
h [label = 'C@_{Enz}'];

node [shape = plaintext];
i [label = 'CO@_{2}'];

#edges
f -> g   [label = 'uptake', fontsize = 10];
g -> f [label = 'death', fontsize = 10];
g -> h [label = 'enzyme production', fontsize = 10];
h -> f  [label = 'enzyme decay', fontsize = 10];
g -> i [label = 'respiration', fontsize = 10];

label='Microbial-enzyme model';

}

subgraph cluster1 {

graph [overlap = false, fontsize = 10, layout = dot, rankdir = LR];

#nodes

node [shape = circle];
c [label = 'C@_{S}'] ;
d [label = 'C@_{MB}'];

node [shape = plaintext];
e [label = 'CO@_{2}'];

#edges
c -> d [label = 'uptake', fontsize = 10];
d -> c [label = 'death', fontsize = 10];
d -> e [label = 'respiration', fontsize = 10];

label='Monod growth';
}

subgraph cluster2 {

graph [overlap = false, fontsize = 10, layout = dot, rankdir = LR];

#nodes
node [shape = circle];
a [label = 'C@_{S}'];

node [shape = plaintext];
b [label = 'CO@_{2}'];

#edges
a -> b [label = 'decay', fontsize = 10];
label = 'First order decay' ;

}
}"

grViz(scheme) %>% export_svg() %>% charToRaw %>% rsvg_pdf("scheme.pdf")

include_graphics("scheme.pdf")

```

```{r Fig. 1, echo=FALSE, resultsw = 'asis', message=FALSE, warning=FALSE, fig.height=14, fig.width=9, fig.cap="_Distribution of microbial biomass carbon data as directly measured by the DNA or cellular protein concentration and calculated by different conversion factors published in the literature [@Baart2008; @Beck2018; @VanDuuren2013; @Marstorp2000, @Christensen1993; Christensen1993; @Yokoyama2017; @VanPutten1995; @Henriksen1996; @Hanegraaf2001]. Middle line corresonds to the median, lower and upper hinges to first and third quartile respectively, lower and upper whisker extends from lower and upper hinge to 1.5 time the interquartile range. Note that the x axis of both plots have different scales._"}

#write.csv(conversions, "./fig1.csv")
fig1<-read.csv("fig1.csv")

ggplot(fig1, aes(Reference, Cmic))+geom_boxplot(cex=0.8, aes(colour=Organism), show.legend = F)+
  facet_wrap(~Proxy, scales="free", nrow=2)+coord_flip()+theme_min+theme(axis.title.y = element_blank())+
  ylab(expression(paste("Microbial biomass carbon (", mu, "mol ", ml^{-1},")")))
```

\
